---
title: "Getting started"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
    theme: flatly
    highlight: espresso
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install the R package

[![Build Status]()]()

This repository is organized as an R package, providing documented functions to reproduce and extend the analysis reported in the publication. 
Note that this package has been written explicitly for this project and may not be suitable for general use. 

This project is setup with a [drake workflow](https://github.com/ropensci/drake), ensuring reproducibility.
Intermediate targets/objects will be stored in a hidden `.drake` directory.

The R library of this project is managed by [renv](https://rstudio.github.io/renv/articles/renv.html).
This makes sure that the exact same package versions are used when recreating the project.
When calling `renv::restore()`, all required packages will be installed with their specific version.

Please note that this project was built with R version 4.0.3 on a Windows 10 operating system.
The renv packages from this project **are not compatible with R versions prior to version 3.6.0.**

**To copy (i.e., clone) this repository to your local machine (for Windows only, please contact author for guidance on other platforms).**  
In Git Bash, the following commands illustrate the procedure to make a local copy of the Github repository in a newly created directory at C://test_globalIRmap :
```{r, engine = 'bash', eval = FALSE}
Mathis@DESKTOP MINGW64 /c/temp
$ cd /c/
Mathis@DESKTOP MINGW64 /c
$ mkdir test_globalIRmap
Mathis@DESKTOP MINGW64 /c
$ cd /c/test_globalIRmap
Mathis@DESKTOP MINGW64 /c/test_globalIRmap
$ git clone https://github.com/messamat/globalIRmap.git
Cloning into 'globalIRmap'...
remote: Enumerating objects: 116, done.
remote: Counting objects: 100% (116/116), done.
remote: Compressing objects: 100% (89/89), done.
remote: Total 7363 (delta 48), reused 75 (delta 19), pack-reused 7247
Receiving objects: 100% (7363/7363), 1.91 GiB | 3.78 MiB/s, done.
Resolving deltas: 100% (925/925), done.
```

In R Studio for Windows, the following procedure can be used:  

* Click on “File” in the menu ribbon  
* Select “New project…”  
* Choose the “Version control” option in the New Project Wizard window.
* Then, select “Git” in the next window.
* In the next window, fill the fields as follows:  
  * Repository URL: https://github.com/messamat/globalIRmap  
  * Project directory name: [will autofill as “globalIRmap”]  
  * Create project as subdirectory of: [choose the directory, e.g., C://test_globalIRmap]  
* Tick “Open in new session” and then click “Create project”.  

**Then open this project in R and run:**  
```{r README-4, eval = FALSE}
renv::restore() # restores all R packages with their specific version
r_make() # recreates the analysis
```

# Structure of the analysis

In the `drake` philosophy, every R object is a "target" with dependencies.
This repository contains more targets than actually needed to replicate the associated publication.
**Future task: create a simplified workflow to strictly reproduce main results**

If you want to replicate the publication, you need to build the following targets:
  -
  -
  -
  -
  
#### Other practical notes

# Notes and resources 

* The [issues tracker](https://github.com/messamat/globalIRmap/issues) is the place to report problems or ask questions  

* See the repository [history](https://github.com/messamat/globalIRmap/commits/master) for a fine-grained view of progress and changes.
